How to Avoid OOTA Without Really Trying

### 2024-10-02 paper/ootavacuous.tex
ootavacuous: Strengthen Section 2 close
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

We have seen several examples showing that semantic dependencies may vary
according to the execution and even the implementation.
This raises several questions, of which the first is:
What exactly is an execution?

>>>>

We have seen several examples showing that semantic dependencies are more
complicated than might first appear, varying according to the execution
and even the implementation.
This raises several questions, of which the first is:
What exactly is an execution?
